### 2017-02-23 manuscript.rmd
added pgls to manuscript

	# Biological
	library( edgeR )
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
	library( agalmar )	# https://github.com/caseywdunn/agalmar
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( fields )
  library( adephylo )
  library( geomorph ) #physig

@@

>>>>

	# Biological
	library( edgeR )
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
	library( agalmar )	# https://github.com/caseywdunn/agalmar
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( fields )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )

@@

PGLS - Sex distribution
```{r pgls_depth_sex, echo=F, message=F, warning=F}
dp_sex <- dpruned_data$Sex
dp_sex = as.numeric(dp_sex)
names(dp_sex) = names(depth_median)
dp_sex[dp_sex==2] = 0        # 0 = Monoecious, 1 = Dioecious
#Vx <- Vy <- Cxy <- rep(0,length(dpruned_tree$tip.label))
#pgls.Ives(dpruned_tree, dp_sex, depth_median, Vx, Vy, Cxy)
pGLS = pgls.Ives(dpruned_tree, rep(dp_sex,3), rep(depth_median,3))
phylolm(depth_median~dp_sex,data=as.data.frame(cbind(depth_median,dp_sex)),phy=dpruned_tree,model="BM",measurement_error=TRUE,boot=100)
gls(dp_sex ~ depth_median)
```
